The Third Bellman Equation

### 2019-01-28 paper/thirdbell.tex

\newcommand{\drho}{\!\setminus\hspace{-.75em}\rho}
\newcommand{\ztar}{z^\mathrm{tar}}
\newcommand{\Nnewt}{N_\mathrm{steps/Newt}}

@@

\paragraph{All rewards at once.} The relationship between $R$ and $V$ is
linear (for a fied policy). The generic representation of $Z$ above
requires computing a model of $V$ for each reward we want to work with.
We can directly exploit the linearity by parameterizing $z$ as
\begin{equation}
z(s_1,s_2)=\langle A(s_1),B(s_2)\rangle
\end{equation}
with some parameterized functions $A$ and $B$ with values in some vector
space with dot product $\langle\cdot,\cdot\rangle$. Intuitively, $A(s_1)$
represents the future of $s_1$, and $B(s_2)$ the past of $s_2$.
Then we have
\begin{equation}
V(s_1)=\langle A(s_1),\E_{s_2\sim \rho} B(s_2)R(s_2)\rangle
\end{equation}
so we can abuse notation and compute
\begin{equation}
B(R)\deq \E_{s_2\sim \rho} B(s_2)R(s_2)
\end{equation}
as the representation of $R$.

>>>>

\newcommand{\drho}{\!\setminus\hspace{-.75em}\rho}
\newcommand{\ztar}{z^\mathrm{tar}}
\newcommand{\Nnewt}{N_\mathrm{steps/Newt}}
\newcommand{\noise}{\epsilon}

@@

\paragraph{All rewards at once.} The relationship between $R$ and $V$ is
linear (for a fied policy). The generic representation of $Z$ above
requires computing a model of $V$ for each reward we want to work with.
We can directly exploit the linearity by parameterizing $z$ as
\begin{equation}
z(s_1,s_2)=\langle A(s_1),B(s_2)\rangle
\end{equation}
with some parameterized functions $A$ and $B$ with values in some vector
space with dot product $\langle\cdot,\cdot\rangle$. Intuitively, $A(s_1)$
represents the future of $s_1$, and $B(s_2)$ the past of $s_2$.
Then we have
\begin{equation}
V(s_1)=\langle A(s_1),\E_{s_2\sim \rho} B(s_2)R(s_2)\rangle
\end{equation}
so we can abuse notation and compute
\begin{equation}
B(R)\deq \E_{s_2\sim \rho} B(s_2)R(s_2)
\end{equation}
as the representation of $R$. Then
\begin{equation}
V(s_1)=\langle A(s_1),B(R)\rangle
\end{equation}

I'm not too sure about this representation. The rank of $Z$ is limited to
the dimension of the vector space, and this may cause problems. An
infinite-dimensional representation can be used, by having $A$ and $B$
take values in a space of $L^2$ functions over some probability space.
Namely, the dot product is
\begin{equation}
z(s_1,s_2)=\E_{\noise} A(s_1,\eps)B(s_2,\eps)
\end{equation}
and we can use as many samples of $\noise$ as we want. Obviously this
adds noise.
